---
title: "CRUZ_MA712_HW7HRA_STATISTICALMODELS_OLOGIT"
output: html_notebook
---
#INTRO

# How does the relationship between a promotion, avg monthly hours worked and time spent with a company effect salary ?

```{r}
library(Zelig)
library(ZeligChoice)
library(faraway)
library(dplyr)
library(tidyr)
library(survival)
```
#Data Upload - Human Resource Data
```{r}
library(radiant.data)
library(readr)
  jquit <- read_csv("/Users/Cruz/Desktop/jquit.csv", col_names = TRUE)
 head(jquit)
```
#Cleaning data set
```{r}
jquit<-na.omit(jquit)
head(jquit)
```
#Running a sample regression to get an idea of some of the variables in the data set.
```{r}
glm.model <- glm(left ~ ., data = jquit, family = "binomial")
summary(glm.model)
```


```{r}
xtabs(~time_spend_company, jquit)

xtabs(~promotion_last_5years, jquit)

xtabs(~salary, jquit)

xtabs(~left, jquit)

```
#Preping data for ologit statistical model.
```{r}
jquit$salary <- factor(jquit$salary, ordered = TRUE,
                         levels = c("low", "medium", "high"))

jquit <- jquit%>%
  mutate(promotion_last_5years = as.factor(promotion_last_5years))
```
#Statistical Model, ologit
```{r}
z.ord <- zelig(salary ~ promotion_last_5years + time_spend_company + average_montly_hours, model = "ologit",
               data = jquit, cite = F)
summary(z.ord)
```

```{r}
x.no <- setx(z.ord, promotion_last_5years = 0)
x.yes <- setx(z.ord, promotion_last_5years = 1)
```

```{r}
s.ord <- sim(z.ord, x = x.no, x1 = x.yes)
summary(s.ord)
```

```{r}
graphics.off()
 par("mar")
 par(mar=c(1,1,1,1))
plot(s.ord)
```


```{r}
c1x <- setx(z.ord, promotion_last_5years = "0", jquit )
c1x1 <- setx(z.ord, promotion_last_5years = "1", jquit)
c1s <- sim(z.ord, x = c1x, x1 = c1x1)
graphics.off()
 par("mar")
```


```{r}
 par(mar=c(1,1,1,1))
plot(c1s)
```




```{r}
d1 <- c1s$get_qi(xvalue="x1", qi="fd")
dfd <- as.data.frame(cbind(d1))
head(dfd)

```



#Difference between those who did and did not receive a promo in last 5 months in Likelihood of being in Low income group = mean = (-0.268) units

```{r}
library(ggplot2)

ggplot(dfd)+
  geom_histogram(aes(x=low),color = "black", fill = "aqua marine1")

```


#Difference between those who did and did not receive a promo in last 5 months in Likelihood of being in Medium income group = mean = (0.126)
```{r}
ggplot(dfd)+
  geom_histogram(aes(x=medium),color = "black", fill = "aqua marine1")
```

#Difference between those who did and did not receive a promo in last 5 months in Likelihood of being in High income group = mean = (0.156)
```{r}
ggplot(dfd)+
  geom_histogram(aes(x=high),color = "black", fill = "aqua marine1") 
```




